### 2023-11-10 manuscript/manuscript.Rmd
improve the wording of the sentence about ESI-MS
Clarify sentence about m/z correlations

Metabolite identification remains one of the main bottlenecks both in time and resources in the analysis of non-targeted mass spectrometry based metabolomics approaches.
Electrospray ionisation mass spectrometry (ESI-MS) is preferred as this is a soft ionisation technique that enables easier compound identification [@domingo2018].
Irrespectively, it is possible for a single metabolite to be represented within ESI-MS spectra by multiple ionisation product adducts and isotopes [@draper2013].

@@

The use of correlations to identify relationships between *m/z* features provides an essential layer of data-driven, internal validation of theoretically derived associations.
For instance, if two features that are posited to have the same composition (eg. a C^13^ relationship) but are not significantly correlated within the matrix, it would then be illogical to infer biological assumptions about associations (eg. metabolic pathway changes) of those features with other putatively assigned features within the matrix.

>>>>

Metabolite identification remains one of the main bottlenecks both in time and resources in the analysis of non-targeted mass spectrometry based metabolomics approaches.
Electrospray ionisation mass spectrometry (ESI-MS) is a soft ionisation technique that simplifies compound identification [@domingo2018].
Irrespectively, it is possible for a single metabolite to be represented within ESI-MS spectra by multiple ionisation product adducts and isotopes [@draper2013].

@@

The use of correlations to identify relationships between *m/z* features provides an essential layer of data-driven, internal validation of theoretically derived associations.
For instance, if two features are posited to have the same molecular formula based on a mass difference equivalent to ^13^C but are not significantly correlated within the matrix, it would then be illogical to infer biological assumptions about other associations (eg. metabolic pathway changes) of those features with other putatively assigned features within the matrix.
